---
title: "team.Rmd"
output: html_document
---

#### Owner's GitHub username: jebirkner
#### Partner's GitHub username: mblount2
#### Repo name: ds202_lab4
#### Due date: Thursday Oct. 24 by 10 pm. 


```{r}
library(tidyverse)
library(readxl)
defense <- read_excel('cyclonesFootball2018.xlsx', sheet='Defensive')
str(defense)
offense <- read_excel('cyclonesFootball2018.xlsx', sheet='Offensive')
bio <- read_excel('cyclonesFootball2018.xlsx', sheet='Biography')
```

```{r}
factor(defense$Name)
factor(defense$Opponent_Opponent)
factor(offense$Name)
factor(offense$Opponent_Opponent)
factor(bio$Name)
```

```{r}
defense = mutate_at(defense, , .funs = as.numeric, .vars = c("Tackles_Solo", "Tackles_ASST","Tackles_TFL", "Tackles_Sack", "Turnover_FF", "Turnover_FR", "Turnover_INT", "Pass_QBH", "Pass_PB"))
str(defense)
```

```{r}
offense = mutate_at(offense, .funs = as.numeric, .vars = names(offense[c(3:12)]))
str(offense)
```

```{r}
bio = mutate_at(bio, .funs = as.numeric, .vars = c("Weight"))
str(bio)
```


3. Separate the `Height` column into two columns. Make sure the newly created columns are numeric. Then create one column that represents `Height` (Hint: Use a unit that works well). Drop any irrelavant columns from this process.

```{r}
bio %>%
  separate(Height, "-")
```


4. By cleaning the three data frames in R, at the end of this step you should have the following three clean data frames: `defClean`, `offClean`, and `bioClean`. Print the structures of these data frames. **Make sure your data types make sense for each variable.**
